HO unification from object language to meta language

### 2024-02-25 paper/main.tex
update tex

\paragraph{Term unification: \Uo vs. \Ue}
TODO

>>>>

\paragraph{Term unification: \Uo vs. \Ue} 
The last but not least important relation we should take care of before
presenting our full algorithm aiming to unify terms of the OL in the ML and
provide the substitution produced in the ML to the OL, is term unification. This
procedure is a more powerful version of the equal predicate, since unification
checks if two terms can be equal be assigning unification variables. In our
representation, variable assignment (or refinement) is performed by modifying
the corresponding substitution mapping. We will not give an implementation of
\Uo in the world of the OL, since we are giving an implementation of it using
our algorithm, see \cref{XX}.

On the other hand, we can
